---
title: "OSRS API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{osrs_api_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(osrsAPI)
```

The `osrs_api` function fetches information on the price of some item from the [Weird Gloop API](https://api.weirdgloop.org/). An item name can be specified with space and improper capitalisation, and an argument can be given to specify how much data is requested. A simple call could look like this to get all historical price data on the Abyssal whip.

```{r}
whip <- osrs_api("Abyssal whip", history = "all")
```

### Possible `history` values

Possible values of `history` are *latest*, *last90d*, *all* or *sample*. It's only possible to query several items for the `latest` option. Fx. the following will return an error:

```{r error = TRUE}
bucket_and_whip <- osrs_api(c("bucket", "Abyssal whip"), history = "all")
```

But the following will work:

```{r}
bucket_and_whip <- osrs_api(c("bucket", "Abyssal whip"), history = "latest")
```

### Extracting information into a useful object

Use the `create_item_data` function to extract the item information and put into a data set. Fx.

```{r}
create_item_data(whip)
```

and

```{r}
create_item_data(bucket_and_whip)
```
